Borel regularity for ODEs and thimble integrals

### 2023-07-25 exp-resurgence.tex
Updates from Overleaf

%then the following diagram is commutative
%\begin{equation}
%\begin{tikzcd}
%I_{\alpha}(z) \arrow[r,"\aexp^\theta"] & \tilde{I}_{\alpha}(z)\arrow[dd,"\borel"]\\
%& \\
%\hat{\iota}_\alpha(\zeta)\arrow[uu, "\laplace^\theta_\alpha "] & \tilde{\iota}_{\alpha}(\zeta) \arrow[l, "\text{sum}"]
%\end{tikzcd}
%\end{equation}
\begin{itemize}
%\item on the one hand take asymptotic expansion of integral via saddle point approximation and then study the Borel Laplace sum of the divergent series [from left upper corners clockwise]
\item on the other hand \textcolor{red}{see that the thimble integral is a generalized Laplace transform (which in certain cases can be rewritten as a usual Laplace transform).}
\item A priori, the Laplace transform of $\hat{\iota}_\alpha(\zeta)$ and $I_{\alpha}(z)$ have the same asymptotic behaviour in a given sector (indeed taking the asymptotic of $I_\alpha(z)$ we \textit{loose} information); however Borel regularity guarantees that $I_{\alpha}(z)=\laplace^{\theta}\hat{\iota}_{\alpha}$ in a given sector.
\item A corollary of [Thm 4] is the fractional derivative formula.
\item \textcolor{red}{As a consequence of Thm 2.4 Pham}, if $f$ and $\nu$ are algebraic, we get that $\hat{\varphi}_\alpha(\zeta)$ to have simple singularities 
\begin{equation}
mmm
\end{equation} 
\end{itemize}
\item \text{[Cor]:} combining our result and the result of Maxim [IHES lectures] (generalizing Pham) we can deduce that Stokes constants for the Borel--Laplace sum of $\tilde{I}_j(z)$ are always integers as they are intersection numbers (use same argument of Maxim). See also the argument of KS21 sec 6.2 in the framework of analytic WCFs. 
\begin{itemize}
\item Prove integrality of Stokes constants using the fractional integral formula vs differential equation (see example in Appendix C) 
\end{itemize}
\end{itemize}
\color{black}

@@

We will illustrate our main results with detailed treatments of several examples: we will mostly focus on degree two ODEs that admit a frame of solutions expressed as thimble integrals (the Airy--Lucas functions, modified Bessel function, Airy function, the anharmonic oscillator...). Then, on the one hand we explicitly solves the integral equation associated to the ODE, building a frame of analytic solutions as Laplace transform of the solutions of the integral equation. On the other hand, our \textit{contour argument} shows how to rewrite explicitly thimble integrals as a Laplace transform and it makes Borel regularity evident directly from explicit computations.

Among the examples we study, some of them have been discussed many times, using different approaches and conventions. We try to give an idea of how all these different treatments fit together. For instance, for the Airy function we will make a comparison with \S 2.2 in \cite{lectures-Marino}, \S 6.14 in \cite{diverg-resurg-i}, and \S 2.2 \cite{kawai-takei}). The anharmonic oscillator was also discussed in (Bender--Wu, Appendix B in \cite{aniceto2019primer}). Other example haven't been discussed much, as for Airy--Lucas functions.

Recently, resurgence theory (first developed by \'Ecalle in the '80) has attracted interests in mathematics and physics as a powerful alternative to Borel summability. Resurgence of lienar ODEs have been intensively studied (see Costin slides for ReNewQuantum, \cite{EcalleIII,loday1994stokes}) and many results are also known for non linear ODEs (see \cite{schiappa-PI}, \cite{costin-PI} \textcolor{magenta}{[check also paper by Ecalle and Sauzin]}). For algebraic thimble integrals of the type we studied in this paper, resurgence of their asymptotic expansion can be understood geometrically (see \cite{Maxim_slide_ERC}, \S 6.2 in \cite{kontsevich2022analyticity}), however for more general exponential integrals (see examples in \cite{Maxim_slide_ERC}) resurgence remains a conjecture. Despite their simplicity, our examples of linear ODEs and of 1-dimensional integrals show some features of resurgence and they are toy model to get a feeling on \'Ecalle formalism.

@@

\color{orange}
\begin{itemize}
\item what does it mean to be Borel regular?
\item when does it happen?
\begin{itemize}
\item State new Borel regularity results
\begin{itemize}
\item Linear, homogeneous ODE with a regular singularity at 0 and irregular singularity at infinity [big idea in {\tt airy-resurgence}]
\begin{itemize}
\item Contextualize with previous work of Braaksma (``Multisummability and Stokes multipliers of linear meromorphic differential equations'')
\item Also contextualize with Balser, Braaksma, Sibuya, and Ramis (``Multisummability of formal power series solutions of linear ordinary differential equations'')
\item Also contextualize with Loday-Richaud
\end{itemize}
\item \emph{Borel regularity} for \textbf{thimbles integrals} can be stated a the commutativity of the following diagram:
\begin{equation}
\begin{tikzcd}
I_{\alpha}(z)\defeq\int_{\mathcal{C}_\alpha}e^{-zf}\nu \arrow[r,"\sim"]\arrow[dd, swap, "\laplace^\theta "] & \tilde{I}_{\alpha}(z)\arrow[dd,"\borel"]\\
& \\
\hat{\iota}_\alpha(\zeta)\arrow[r,equal,swap, "\text{sum}"] & \tilde{\iota}_{\alpha}(\zeta) 
\end{tikzcd}
\end{equation}
\item A priori, the Laplace transform of $\hat{\iota}_\alpha(\zeta)$ and $I_{\alpha}(z)$ have the same asymptotic behavior in a given sector (indeed taking the asymptotic of $I_\alpha(z)$ we \textit{loose} information); however Borel regularity guarantees that $I_{\alpha}(z)=\laplace^{\theta}\hat{\iota}_{\alpha}$ in a given sector.
\item fractional derivative formula
\item Conjecturally, we expect $\hat{\varphi}_\alpha(\zeta)$ to have simple singularities. 
\item in the examples, $\hat{\varphi}_\alpha(\zeta)$ turn out be an hypergeometric function of type ${}_pF_{p-1}$ where $p$ is the number of critical values. 
\item We expect that hypergeometric functions play a special role in resurgence theory as they may always appear when there are only finitely many singularities.
\item \textcolor{magenta}{maybe we can say more about algebraic hypergeometric functions}
\end{itemize}
%\item Recall Watson condition (old): Let $R_N$ be the difference between a function and the partial sum
%\[ \frac{\varphi_0}{z} + \frac{\varphi_1}{z^2} + \frac{\varphi_2}{z^3} + \ldots + \frac{\varphi_{N-2}}{z^{N-1}} \]
%of its asymptotic series. Watson showed a century ago that the function is Borel regular whenever there's a constant $c \in (0, \infty)$ with
%\[ |R_N| \le \frac{c^{N+1} N!}{|z|^N} \]
%over all orders $N$ and all $z$ in a wide enough wedge around infinity.
\end{itemize}
\end{itemize}

@@

\subsection{Fractional derivative formula}
\begin{itemize}
\item formula \eqref{formula1} Theorem~\ref{thm:maxim} says that for a certain class of exponential integrals
\[ I(z) = \int_\Gamma e^{-zf}\;\nu, \]
the inverse Laplace transform is the $\tfrac{3}{2}$ derivative of $\nu/df$ at $\zeta=f$.
\item the asymptotic expansion of $I(z)$ is a resurgent function.
\item Is it always a \emph{simple} resurgent function?
\begin{itemize}
\item \textbf{Maxim belies it is in general, and indeed in our examples, we get simple resurgent functions. But how to prove it in general?}
\end{itemize} 
\end{itemize}

@@

\subsubsection{Contour argument for Airy-Lucas functions}\label{contour-argument-AL}
\textcolor{orange}{[\textbf{New phrasing for rewrite:} The critical point splits the thimble $\Lambda$ into two pieces: the {\em incoming} branch, where the orientation of the thimble runs toward the critical point, and the {\em outgoing} branch, where the orientation points away.]}

@@

The contour argument we describe in Section~\ref{contour-argument-AL} has to be generalized, as we will discuss in the following Section~\ref{countable-cover}.

@@

\begin{equation}
    K_0(z)=-\frac{1}{2}\int_1^\infty e^{-z\zeta} \, \left(\frac{\zeta-1}{2}\right)^{-1/2} \,\, {}_2F_1\left(\frac{1}{2}, \frac{1}{2};\frac{1}{2};\frac{1-\zeta}{2}\right)  d\zeta =  \int_1^\infty \frac{e^{-z\zeta}}{\sqrt{\zeta^2-1}} \, d\zeta .
\end{equation}
\textcolor{orange}{[can we use (51) directly? It seems to me that if I try the contour argument from the integral expression directly, I'm not able to write write $1/\sinh(it)$ as a function of $\zeta$. ]}

@@

\subsubsection{Contour argument for higher Airy of degree $3$}

@@

and we denote $\hat{w}_2(\zeta)=c_2\,\, {}_3F_2\left(\mathbf{a};\mathbf{b};\left(\tfrac{3}{2}\zeta+1\right)^2\right)$. The equation \eqref{w3} differes from \eqref{w2} for few signs: we find that its Borel transform is

@@

\subsubsection{Fractional derivative formula}

@@

\[ I_j(z) = \int_{\Lambda_j} \exp\left[-z\big(u^3 + pu + q)\right]\,du \]

where $\Lambda_j$ is a thimble in $H_{1}^{B,z}$ through a critical point of $f$. We can distinguish between the case when $f$ has two distinct critical points $x_+, x_-$ and only one critical point $x$. In both cases, we will compute the differential equation satisfied by $I$.

\begin{lemma}
    Let $f(u)=u^3+pu+q$, 
    \begin{itemize}
        \item if $p\neq 0$, then $I_{\pm}(z)$ solves 
        \begin{equation}\label{eqn:degree-3-poly-2roots}
            \left[\partial_z^2 +2q \partial_z+\left(\frac{4p^3}{27}+q^2\right)+\frac{1}{z}\left(\partial_z +q \right)-\frac{1}{9z^2}\right]\Phi=0
        \end{equation}
        \item  if $p=0$, then $I(z)$ solves
        \begin{equation}\label{eqn:degree-3-poly-1root}
            \left[\partial_z+q+\frac{1}{3z}\right]I=0
        \end{equation}
    \end{itemize}
\end{lemma}
\begin{proof}
    The proof follows from a direct computation. 
\end{proof}

Let us first assume $p\neq 0$, then $x_{\pm}=\pm\sqrt{-p/3}$ and the critical values are $\alpha_{\pm}=f(x_\pm)$. Notice that equation \eqref{eqn:degree-3-poly-2roots} admits slight solutions as $\tau_\pm=\frac{1}{2}$ (recall the definition of $\tau\pm=\frac{Q(-\alpha_\pm)}{P'(-\alpha_\pm)}$ as in Section \ref{borel_reg-ODE}), thus, for $\theta=-\arg z$, $\laplace_{\zeta,f(\alpha_\pm)}^{\theta}v_\pm$ solves \eqref{eqn:degree-3-poly-2roots} if and only $v_\pm$ solves

\begin{equation}\label{eqn:deg3-borel-ODE}
    \left[\Big[\zeta^2-2q\zeta+\big(\frac{4p^3}{27}+q^2\big)\Big]\partial_\zeta^2+3(\zeta-q)\partial_\zeta+\frac{8}{9}\right]v_\pm=0
\end{equation}

Let us find a solution of \eqref{eqn:deg3-borel-ODE} slight at $\zeta=\alpha_+$: in the new coordinate $\zeta_+:=\zeta-\alpha_+$, equation \eqref{eqn:deg3-borel-ODE} becomes

\begin{equation*}
    \left[\zeta_+ (\zeta_+ + \frac{4}{3}p\, x_+)\partial_{\zeta_+}^2+ \left[2p\, x_++3\zeta_{+}\right]\partial_{\zeta_+} +\frac{8}{9} \right]v_+=0
\end{equation*}

which is an hypergeometric equation in the coordinate $\xi=-\frac{3}{4p\,x_+}\zeta_+$

\begin{equation*}
    \left[\xi (1-\xi)\partial_{\xi}^2+ 3\big(\frac{1}{2}-\xi\big)\partial_{\xi}-\frac{8}{9} \right]v_+=0
\end{equation*}

and it admits a slight solution

\begin{align*}
    v_+ &= \xi^{-1/2}\, {}_2F_1\left(\frac{1}{6},\frac{5}{6} ;\frac{3}{2};1-\xi\right)\\
    &=\left(\frac{3}{4p\,x_+}\zeta_+\right)^{-1/2}\, {}_2F_1\left(\frac{1}{6},\frac{5}{6} ;\frac{3}{2};1-\frac{3}{4p\,x_+}\zeta_+\right). 
\end{align*}

Notice that $v_+$ is a hypergeometric function with the same parameters as the hypergeometric function $v_1$ in the example of Airy \S \ref{pos-root}. Similarly for $\zeta_-=\zeta-\alpha_-$

\begin{equation*}
    v_- =\left(\frac{3}{4p\,x_-}\zeta_-\right)^{-1/2}\, {}_2F_1\left(\frac{1}{6},\frac{5}{6} ;\frac{3}{2};1-\frac{3}{4p\,x_-}\zeta_-\right). 
\end{equation*}

When $p=0$, the critical point of $f$ is $x=0$ and we can argue as before: $\laplace_{\zeta,\alpha}^{\theta}v$ is a solution of \eqref{eqn:degree-3-poly-1root} if and only if $v$ is a solution of

@@

namely $v=(\zeta-q)^{-2/3}=\zeta_q^{-2/3}={}_2F_1\left(a,\frac{2}{3};a;1-\zeta_q\right)$, where $\zeta_q=\zeta-q$ and $a\in\C$ is a free parameter. The same result is confirmed by the contour argument which in this simple case reads

@@

\textcolor{orange}{[It'd be nice to have the contour argument for $p\neq 0$ too, however we don't have the same nice coordinates as in the other examples--maybe we can do a change of coordinates to recover $K_{1/3}$ as suggested below.]}
\color{DarkTurquoise}
\begin{itemize}
\item Reduce to
\[ I(z) = \int \exp\left[-z\big(u^3 + pu + q)\right]\,du \]
using change of coordinate.
\item When $p \neq 0$, can reduce further to
\[ I(z) = p^{1/2} e^{-qz} K_{1/3}(p^{3/2} z). \]
\item As $p$ goes to zero, $I(z)$ degenerates to
\[ \left(\tfrac{1}{2}\right)^{2/3} e^{-qz} \Gamma(\tfrac{1}{3}) z^{-1/3} = \left(\tfrac{1}{2}\right)^{2/3} e^{-qz} \laplace_{\zeta,0}(\zeta^{-2/3}) = \left(\tfrac{1}{2}\right)^{2/3} \laplace_{\zeta_{-q},q}(\zeta^{-2/3}). \]
\end{itemize}

@@

\item Contour argument

@@

\item Using fractional derivative formula and Borel transform computation [{\tt draft2}]

@@

\subsection{Contour argument for the Airy function}\label{contour-argument}
Generalizing from Section~\ref{contour-argument-AL}, we can recast integral~\eqref{integral:mod-bessel} into the $\zeta$ plane by setting $-\zeta = 4u^3 - 3u$. Projecting $z^{-1/3} \Gamma$ to a contour $\gamma_z$ in the $\zeta$ plane and choosing the branch of $u$ that lifts $\gamma_z$ back to $z^{-1/3} \Gamma$, we have
\begin{equation}\label{integral:mod-bessel-zeta}
K = \frac{i}{\sqrt{3}} \int_{\gamma_z} e^{-z\zeta}\frac{d\zeta}{4u^2 - 1}.
\end{equation}
For $z \in (0, \infty)$, the contour $\gamma_z$ runs clockwise around $[1, \infty)$, as shown below. Let's assume $z \in (0, \infty)$ for the rest of the section. \textcolor{magenta}{[Our conclusions should probably hold whenever $\operatorname{Re}(z) > 0$.]}
\begin{center}
\includegraphics{figures/zeta_contour_3.pdf} \\[1em]
{\small The contour $\gamma_1$ in the $\zeta$ plane.}
\end{center}

@@

In summary, the contour integration method of solving equation~\eqref{eqn:reg-mod-bessel} is associated with the basis
\begin{align*}
g_{1} & = {}_2F_1\big(\tfrac{2}{3}, \tfrac{4}{3}; \tfrac{3}{2}; \xi\big) \\
g_{-1} & = {}_2F_1\big(\tfrac{2}{3}, \tfrac{4}{3}; \tfrac{3}{2}; 1-\xi\big)
\end{align*}
of solutions for equation~\eqref{diff-eq:spatial-mod-bessel}, given by formulas 15.10.11 and 15.10.13 from \cite{dlmf}. These solutions contribute the poles at $\xi = 1$ and $\xi = 0$, respectively, of a generic solution.

>>>>

%then the following diagram is commutative
%\begin{equation}
%\begin{tikzcd}
%I_{\alpha}(z) \arrow[r,"\aexp^\theta"] & \tilde{I}_{\alpha}(z)\arrow[dd,"\borel"]\\
%& \\
%\hat{\iota}_\alpha(\zeta)\arrow[uu, "\laplace^\theta_\alpha "] & \tilde{\iota}_{\alpha}(\zeta) \arrow[l, "\text{sum}"]
%\end{tikzcd}
%\end{equation}
\begin{itemize}
%\item on the one hand take asymptotic expansion of integral via saddle point approximation and then study the Borel Laplace sum of the divergent series [from left upper corners clockwise]
\item on the other hand \textcolor{red}{see that the thimble integral is a generalized Laplace transform (which in certain cases can be rewritten as a usual Laplace transform).}
\item A priori, the Laplace transform of $\hat{\iota}_\alpha(\zeta)$ and $I_{\alpha}(z)$ have the same asymptotic behaviour in a given sector (indeed taking the asymptotic of $I_\alpha(z)$ we \textit{loose} information); however Borel regularity guarantees that $I_{\alpha}(z)=\laplace^{\theta}\hat{\iota}_{\alpha}$ in a given sector.
\item A corollary of [Thm 4] is the thimble projection formula.
\item \textcolor{red}{As a consequence of Thm 2.4 Pham}, if $f$ and $\nu$ are algebraic, we get that $\hat{\varphi}_\alpha(\zeta)$ to have simple singularities 
\begin{equation}
mmm
\end{equation} 
\end{itemize}
\item \text{[Cor]:} combining our result and the result of Maxim [IHES lectures] (generalizing Pham) we can deduce that Stokes constants for the Borel--Laplace sum of $\tilde{I}_j(z)$ are always integers as they are intersection numbers (use same argument of Maxim). See also the argument of KS21 sec 6.2 in the framework of analytic WCFs. 
\begin{itemize}
\item Prove integrality of Stokes constants using the fractional integral formula vs differential equation (see example in Appendix C) 
\end{itemize}
\end{itemize}
\color{black}

@@

We will illustrate our main results with detailed treatments of several examples: we will mostly focus on degree two ODEs that admit a frame of solutions expressed as thimble integrals (the Airy--Lucas functions, modified Bessel function, Airy function, the anharmonic oscillator...). Then, on the one hand, we explicitly solve the integral equation associated with the ODE, building a frame of analytic solutions as the Laplace transform of the solutions of the integral equation. On the other hand, our \textit{thimble projection reasoning} shows how to rewrite explicitly thimble integrals as a Laplace transform and it makes Borel regularity evident directly from explicit computations.

Among the examples we study, some of them have been discussed many times, using different approaches and conventions. We try to give an idea of how all these different treatments fit together. For instance, for the Airy function we will make a comparison with \S 2.2 in \cite{lectures-Marino}, \S 6.14 in \cite{diverg-resurg-i}, and \S 2.2 \cite{kawai-takei}). The anharmonic oscillator was also discussed in (Bender--Wu, Appendix B in \cite{aniceto2019primer}). Other examples haven't been discussed much, as for Airy--Lucas functions.

Recently, resurgence theory (first developed by \'Ecalle in the '80) has attracted interest in mathematics and physics as a powerful alternative to Borel summability. The resurgence of linear ODEs have been intensively studied (see Costin slides for ReNewQuantum, \cite{EcalleIII,loday1994stokes}) and many results are also known for non-linear ODEs (see \cite{schiappa-PI}, \cite{costin-PI} \textcolor{magenta}{[check also paper by Ecalle and Sauzin]}). For algebraic thimble integrals of the type we studied in this paper, resurgence of their asymptotic expansion can be understood geometrically (see \cite{Maxim_slide_ERC}, \S 6.2 in \cite{kontsevich2022analyticity}), however for more general exponential integrals (see examples in \cite{Maxim_slide_ERC}) resurgence remains a conjecture. Despite their simplicity, our examples of linear ODEs and of 1-dimensional integrals show some features of resurgence and they are toy-model to get a feeling of \'Ecalle formalism.

@@

\color{orange}
\begin{itemize}
\item what does it mean to be Borel regular?
\item when does it happen?
\begin{itemize}
\item State new Borel regularity results
\begin{itemize}
\item Linear, homogeneous ODE with a regular singularity at 0 and irregular singularity at infinity [big idea in {\tt airy-resurgence}]
\begin{itemize}
\item Contextualize with previous work of Braaksma (``Multisummability and Stokes multipliers of linear meromorphic differential equations'')
\item Also contextualize with Balser, Braaksma, Sibuya, and Ramis (``Multisummability of formal power series solutions of linear ordinary differential equations'')
\item Also contextualize with Loday-Richaud
\end{itemize}
\item \emph{Borel regularity} for \textbf{thimbles integrals} can be stated a the commutativity of the following diagram:
\begin{equation}
\begin{tikzcd}
I_{\alpha}(z)\defeq\int_{\mathcal{C}_\alpha}e^{-zf}\nu \arrow[r,"\sim"]\arrow[dd, swap, "\laplace^\theta "] & \tilde{I}_{\alpha}(z)\arrow[dd,"\borel"]\\
& \\
\hat{\iota}_\alpha(\zeta)\arrow[r,equal,swap, "\text{sum}"] & \tilde{\iota}_{\alpha}(\zeta) 
\end{tikzcd}
\end{equation}
\item A priori, the Laplace transform of $\hat{\iota}_\alpha(\zeta)$ and $I_{\alpha}(z)$ have the same asymptotic behavior in a given sector (indeed taking the asymptotic of $I_\alpha(z)$ we \textit{loose} information); however Borel regularity guarantees that $I_{\alpha}(z)=\laplace^{\theta}\hat{\iota}_{\alpha}$ in a given sector.
\item thimble projection formula
\item Conjecturally, we expect $\hat{\varphi}_\alpha(\zeta)$ to have simple singularities. 
\item in the examples, $\hat{\varphi}_\alpha(\zeta)$ turn out be an hypergeometric function of type ${}_pF_{p-1}$ where $p$ is the number of critical values. 
\item We expect that hypergeometric functions play a special role in resurgence theory as they may always appear when there are only finitely many singularities.
\item \textcolor{magenta}{maybe we can say more about algebraic hypergeometric functions}
\end{itemize}
%\item Recall Watson condition (old): Let $R_N$ be the difference between a function and the partial sum
%\[ \frac{\varphi_0}{z} + \frac{\varphi_1}{z^2} + \frac{\varphi_2}{z^3} + \ldots + \frac{\varphi_{N-2}}{z^{N-1}} \]
%of its asymptotic series. Watson showed a century ago that the function is Borel regular whenever there's a constant $c \in (0, \infty)$ with
%\[ |R_N| \le \frac{c^{N+1} N!}{|z|^N} \]
%over all orders $N$ and all $z$ in a wide enough wedge around infinity.
\end{itemize}
\end{itemize}

@@

\subsection{thimble projection formula}
\begin{itemize}
\item formula \eqref{formula1} Theorem~\ref{thm:maxim} says that for a certain class of exponential integrals
\[ I(z) = \int_\Gamma e^{-zf}\;\nu, \]
the inverse Laplace transform is the $\tfrac{3}{2}$ derivative of $\nu/df$ at $\zeta=f$.
\item the asymptotic expansion of $I(z)$ is a resurgent function.
\item Is it always a \emph{simple} resurgent function?
\begin{itemize}
\item \textbf{Maxim belies it is in general, and indeed in our examples, we get simple resurgent functions. But how to prove it in general?}
\end{itemize} 
\end{itemize}

@@

\subsubsection{Thimble projection technique for Airy-Lucas functions}\label{contour-argument-AL}
\textcolor{orange}{[\textbf{New phrasing for rewrite:} The critical point splits the thimble $\Lambda$ into two pieces: the {\em incoming} branch, where the orientation of the thimble runs toward the critical point, and the {\em outgoing} branch, where the orientation points away.]}

@@

The thimble projection reasoning we describe in Section~\ref{contour-argument-AL} has to be generalized, as we will discuss in the following Section~\ref{countable-cover}.

@@

\begin{equation}
    K_0(z)=-\frac{1}{2}\int_1^\infty e^{-z\zeta} \, \left(\frac{\zeta-1}{2}\right)^{-1/2} \,\, {}_2F_1\left(\frac{1}{2}, \frac{1}{2};\frac{1}{2};\frac{1-\zeta}{2}\right)  d\zeta =  \int_1^\infty \frac{e^{-z\zeta}}{\sqrt{\zeta^2-1}} \, d\zeta .
\end{equation}
\textcolor{orange}{[can we use (51) directly? It seems to me that if I try the thimble projection reasoning from the integral expression directly, I'm not able to write $1/\sinh(it)$ as a function of $\zeta$. ]}

@@

\subsubsection{thimble projection reasoning for higher Airy of degree $3$}

@@

and we denote $\hat{w}_2(\zeta)=c_2\,\, {}_3F_2\left(\mathbf{a};\mathbf{b};\left(\tfrac{3}{2}\zeta+1\right)^2\right)$. The equation \eqref{w3} differs from \eqref{w2} for few signs: we find that its Borel transform is

@@

\subsubsection{thimble projection formula}

@@

\[ I_j(z) = \int_{\Lambda_j} \exp\left[z\big(u^3 + pu + q)\right]\,du \]

where $\Lambda_j$ is a thimble in $H_{1}^{B,z}$ through a critical point of $f$. We can distinguish between the case when $f$ has two distinct critical points $x_+, x_-$ and only one critical point $x$, which correspond respectively to the case $p\neq 0$ and $p=0$. \footnote{Equivalently, the difference between the generic case ($p\neq 0$) and the degenerate one ($p=0$) is visible from the ODE perspective as in the former case $I$ is a solution of degree two ODE \[\left[\partial_z^2 +2q \partial_z+\left(\frac{4p^3}{27}+q^2\right)+\frac{1}{z}\left(\partial_z +q \right)-\frac{1}{9z^2}\right]\Phi=0,\] while in the latter, $I$ solves a degree one ODE (see \eqref{eqn:degree-3-poly-1root}).}

Recall that translations and scaling-rotations act naturally on the image of $f\colon X\to \C$ ($f$ not necessarily a degree three polynomial), and their action transforms the thimble integral $I_j$ in the following ways:

\begin{itemize}
    \item \textbf{Action of translations:} let $q\in\C$, post-composing with translation of $q$ maps $f\to f+q$, thus 
    \begin{align*}
        \int_{\Lambda_j}e^{z (f+q)} \nu &= e^{qz} I_j(z)
    \end{align*}
    \item  \textbf{Action of scaling-rotations:} let $\gamma\in\C$, post-composing with scaling-rotations by $\gamma$ maps $f\to \gamma\cdot f$, thus 
    \begin{align*}
        \int_{\Lambda_j}e^{z (\gamma\cdot f)} \nu &= I_j(z \gamma)
    \end{align*}
\end{itemize}

In particular, we can always reduce to study the thimble integral in simpler situations.

As an example, every degree three polynomial with distinct critical points can be transformed in the Chebyshev polynomial $T_3(t)=4 t^3-3t$, implying that the thimble integral $I_+$ can be transformed into the Airy--Lucas integral with parameter $m=1, n=3$. This follows by post-composing $f$ with a translation of $-q$ followed by a scaling-rotation of $\frac{ -i 3^{3/2}}{2 p^{3/2}}$

\begin{align*}
    f-q &= u^3 + pu \\
    (f-q) \cdot \frac{ -i 3^{3/2}}{2 p^{3/2}} &= 4 \Big(\sqrt{-\tfrac{3}{p}} \tfrac{u}{2} \Big)^{3} - 3\Big(\sqrt{-\tfrac{3}{p}} \tfrac{u}{2} \Big) \\
    &= 4 t^3- 3t 
\end{align*}

with $t= \sqrt{-\frac{3}{p}} \frac{u}{2}$. Then the thimble integral $I_+$ gets transformed into

\begin{align*}
    e^{-zq} I_+\left(-\tfrac{i 3^{3/2}}{2 p^{3/2}} z\right)&= \int_{\Lambda_+} e^{z (4t^3-3t)} du\\
    &= 2\sqrt{-\tfrac{p}{3}} \int_{\Lambda_+} e^{z (4t^3-3t)} dt \\
    &= 2\sqrt{-\tfrac{p}{3}} K_{1/3}(z). 
\end{align*}

In particular, when $p\neq 0$, the thimble integral $I_+$ can be studied following the analysis of Appendix \ref{airy-appendix}. 
%In both cases, we will compute the differential equation satisfied by $I$.

%\begin{lemma}
 %Let $f(u)=u^3+pu+q$, 
  %  \begin{itemize}
   %     \item if $p\neq 0$, then $I_{\pm}(z)$ solves 
    %    \begin{equation}\label{eqn:degree-3-poly-2roots}
    %        \left[\partial_z^2 +2q \partial_z+\left(\frac{4p^3}{27}+q^2\right)+\frac{1}{z}\left(\partial_z +q \right)-\frac{1}{9z^2}\right]\Phi=0
    %    \end{equation}
    %    \item  if $p=0$, then $I(z)$ solves
     %   \begin{equation}\label{eqn:degree-3-poly-1root}
      %      \left[\partial_z+q+\frac{1}{3z}\right]I=0
      %  \end{equation}
    %\end{itemize}
%\end{lemma}
%\begin{proof}
 %   The proof follows from a direct computation. 
%\end{proof}

%Let us first assume $p\neq 0$, then $x_{\pm}=\pm\sqrt{-p/3}$ and the critical values are $\alpha_{\pm}=f(x_\pm)$. Notice that equation \eqref{eqn:degree-3-poly-2roots} admits slight solutions as $\tau_\pm=\frac{1}{2}$ (recall the definition of $\tau\pm=\frac{Q(-\alpha_\pm)}{P'(-\alpha_\pm)}$ as in Section \ref{borel_reg-ODE}), thus, for $\theta=-\arg z$, $\laplace_{\zeta,f(\alpha_\pm)}^{\theta}v_\pm$ solves \eqref{eqn:degree-3-poly-2roots} if and only $v_\pm$ solves

%\begin{equation}\label{eqn:deg3-borel-ODE}
 %   \left[\Big[\zeta^2-2q\zeta+\big(\frac{4p^3}{27}+q^2\big)\Big]\partial_\zeta^2+3(\zeta-q)\partial_\zeta+\frac{8}{9}\right]v_\pm=0
%\end{equation}

%Let us find a solution of \eqref{eqn:deg3-borel-ODE} slight at $\zeta=\alpha_+$: in the new coordinate $\zeta_+:=\zeta-\alpha_+$, equation \eqref{eqn:deg3-borel-ODE} becomes

%\begin{equation*}
 %   \left[\zeta_+ (\zeta_+ + \frac{4}{3}p\, x_+)\partial_{\zeta_+}^2+ \left[2p\, x_++3\zeta_{+}\right]\partial_{\zeta_+} +\frac{8}{9} \right]v_+=0
%\end{equation*}

%which is an hypergeometric equation in the coordinate $\xi=-\frac{3}{4p\,x_+}\zeta_+$

%\begin{equation*}
 %   \left[\xi (1-\xi)\partial_{\xi}^2+ 3\big(\frac{1}{2}-\xi\big)\partial_{\xi}-\frac{8}{9} \right]v_+=0
%\end{equation*}

%and it admits a slight solution \textcolor{red}{the solution should match with the one of airy, so choose $w_2$ in DLMf list and not $w_1$}

%\begin{align*}
 %   v_+ &= \xi^{-1/2}\, {}_2F_1\left(\frac{1}{6},\frac{5}{6} ;\frac{3}{2};1-\xi\right)\\
  %  &=\left(\frac{3}{4p\,x_+}\zeta_+\right)^{-1/2}\, {}_2F_1\left(\frac{1}{6},\frac{5}{6} ;\frac{3}{2};1-\frac{3}{4p\,x_+}\zeta_+\right). 
%\end{align*}

%Notice that $v_+$ is a hypergeometric function with the same parameters as the hypergeometric function $v_1$ in the example of Airy \S \ref{pos-root}. Similarly for $\zeta_-=\zeta-\alpha_-$

%\begin{equation*}
%    v_- =\left(\frac{3}{4p\,x_-}\zeta_-\right)^{-1/2}\, {}_2F_1\left(\frac{1}{6},\frac{5}{6} ;\frac{3}{2};1-\frac{3}{4p\,x_-}\zeta_-\right). 
%\end{equation*}

We then consider the case when $p=0$, and we study it both as a solution of an ODE and as a thimble integral.

First, notice that $I(z)$ solves
       \begin{equation}\label{eqn:degree-3-poly-1root}
          \left[\partial_z+q+\frac{1}{3z}\right]I=0
       \end{equation}

and we can find a Borel regular solution following the argument of \S \ref{big-idea}: $\laplace_{\zeta,\alpha}^{\theta}v$ is a solution of \eqref{eqn:degree-3-poly-1root} if and only if $v$ is a solution of

@@

namely $v=(\zeta-q)^{-2/3}=\zeta_q^{-2/3}={}_2F_1\left(a,\frac{2}{3};a;1-\zeta_q\right)$, where $\zeta_q=\zeta-q$ and $a\in\C$ is a free parameter.

The result is confirmed by the thimble projection reasoning which in this simple case reads

@@

\color{DarkTurquoise}
\begin{itemize}
\item As $p$ goes to zero, $I(z)$ degenerates to
\[ \left(\tfrac{1}{2}\right)^{2/3} e^{-qz} \Gamma(\tfrac{1}{3}) z^{-1/3} = \left(\tfrac{1}{2}\right)^{2/3} e^{-qz} \laplace_{\zeta,0}(\zeta^{-2/3}) = \left(\tfrac{1}{2}\right)^{2/3} \laplace_{\zeta_{-q},q}(\zeta^{-2/3}). \]
\end{itemize}

@@

\item thimble projection reasoning

@@

\item Using thimble projection formula and Borel transform computation [{\tt draft2}]

@@

\subsection{thimble projection reasoning for the Airy function}\label{contour-argument}
Generalizing from Section~\ref{contour-argument-AL}, we can recast integral~\eqref{integral:mod-bessel} into the $\zeta$ plane by setting $-\zeta = 4u^3 - 3u$. Projecting $z^{-1/3} \Gamma$ to a contour $\gamma_z$ in the $\zeta$ plane and choosing the branch of $u$ that lifts $\gamma_z$ back to $z^{-1/3} \Gamma$, we have
\begin{equation}\label{integral:mod-bessel-zeta}
K = \frac{i}{\sqrt{3}} \int_{\gamma_z} e^{-z\zeta}\frac{d\zeta}{4u^2 - 1}.
\end{equation}
For $z \in (0, \infty)$, the contour $\gamma_z$ runs clockwise around $[1, \infty)$, as shown below. Let's assume $z \in (0, \infty)$ for the rest of the section. \textcolor{magenta}{[Our conclusions should probably hold whenever $\operatorname{Re}(z) > 0$.]}
\begin{center}
\includegraphics{figures/zeta_contour_3.pdf} \\[1em]
{\small The contour $\gamma_1$ in the $\zeta$ plane.}
\end{center}

@@

In summary, the thimble projection technique of solving equation~\eqref{eqn:reg-mod-bessel} is associated with the basis
\begin{align*}
g_{1} & = {}_2F_1\big(\tfrac{2}{3}, \tfrac{4}{3}; \tfrac{3}{2}; \xi\big) \\
g_{-1} & = {}_2F_1\big(\tfrac{2}{3}, \tfrac{4}{3}; \tfrac{3}{2}; 1-\xi\big)
\end{align*}
of solutions for equation~\eqref{diff-eq:spatial-mod-bessel}, given by formulas 15.10.11 and 15.10.13 from \cite{dlmf}. These solutions contribute the poles at $\xi = 1$ and $\xi = 0$, respectively, of a generic solution.
